Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-01-03 paper/paper.tex
20200103 10:45:50

In this manuscript, by combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the $J-K-\Gamma$ model. \textcolor{red}{$\cdots\cdots$}

The rest of the paper is organized as follows: \textcolor{red}{$\cdots\cdots$}

@@

\section{Moment Direction-Exact Diagonalization Results}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig. \ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction determined for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively. (c)-{f} Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D}, resepctively.}
     \label{fig:Proabilities}
\end{figure}

@@

The main effect of $\Gamma$ term on \emph{Stripe-A} and \emph{Stripe-D} is tilting the moment orientation away from the cubic axes directions, yielding \emph{Stripe-B} and \emph{Stripe-C}. Fig. \ref{fig:Proabilities}(e) is a representative probability map for \emph{Stripe-B}. The probability takes maximum value at the directions determined by Eq.\eqref{eq:S1}.
\textcolor{red}{$\cdots \cdots$}

>>>>

The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization methods are introduced in Section II. Section III discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states. The global phase diagram of the quantum model is presented in Section IV along with a discussion of its phases. In Section V, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.

@@

\section{Moment Direction-Exact Diagonalization Results}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig. \ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively. (c)-(f) Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C} and \emph{Stripe-D} phase, respectively.}
\end{figure}

@@

The main effect of $\Gamma$ term on the \emph{Stripe-A} and \emph{Stripe-D} phase is tilting the moment orientation away from the cubic axes directions, yielding the \emph{Stripe-B} and \emph{Stripe-C} phase. Fig. \ref{fig:Proabilities}(e) is a representative probability map for the \emph{Stripe-B} phase. The probability takes maximum value at the direction determined by Eq.\eqref{eq:S1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$. On the other hand, the case of the \emph{Stripe-C} phase is rather different. The probability is clearly peaked at the direction given by Eq.\eqref{eq:S0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig. \ref{fig:Proabilities}(d)). Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.
